\section{Compressed Sensing with Quantum Correlations}
\label{sec:compressed_sensing}

Compressed sensing (CS) provides a natural framework for quantum imaging, where measurements are inherently limited by photon budgets and detector constraints. This section reviews the integration of deep learning with CS approaches that exploit quantum correlations.

\subsection{Quantum Compressed Sensing Fundamentals}

\citet{katz2009} demonstrated that ghost imaging can be formulated as a compressed sensing problem, achieving image reconstruction from significantly fewer measurements than the Nyquist limit by exploiting the sparsity of natural images. In this framework, the bucket detector measurements constitute the compressed observations $\mathbf{y} = \Phi \mathbf{x}$, where $\Phi$ is determined by the illumination patterns and $\mathbf{x}$ is the image to be recovered.

The quantum advantage in this context arises from two sources. First, entangled photon pairs can provide measurement matrices with favourable incoherence properties, naturally satisfying the conditions required for CS recovery \citep{donoho2006, candes2006}. Second, quantum correlations enable noise rejection through coincidence detection, effectively improving the signal-to-noise ratio of each measurement.

\subsection{Neural Network Enhanced CS Reconstruction}

Traditional CS recovery algorithms (e.g., basis pursuit, iterative hard thresholding) are computationally expensive and require careful tuning of regularisation parameters. Deep learning offers two strategies for improvement: (i)~\emph{purely data-driven} approaches that learn a direct mapping from compressed measurements to images, bypassing explicit sparsity assumptions; and (ii)~\emph{deep unfolding} approaches that parameterise iterative CS algorithms as neural networks, combining the interpretability of model-based methods with the flexibility of learned parameters.

Deep unfolding originated with LISTA \citep{gregor2010}, which unfolded the iterations of the Iterative Shrinkage-Thresholding Algorithm (ISTA) into a fixed-depth feedforward network. Rather than using the fixed matrices prescribed by standard ISTA, all weight matrices and shrinkage thresholds at each layer are treated as learnable parameters trained via backpropagation. The resulting network produces accurate sparse codes in a small, fixed number of forward passes, achieving orders-of-magnitude speedup over traditional ISTA. \citet{yang2016} extended this idea to the Alternating Direction Method of Multipliers (ADMM) for CS-MRI reconstruction, mapping each ADMM iteration to a network layer with learnable transforms, penalty parameters, and multipliers. \citet{zhang2018ista} proposed ISTA-Net+, which performs reconstruction in the residual domain to exploit the higher compressibility of image residuals, achieving state-of-the-art CS reconstruction quality on natural images.

\citet{ongie2020} provide a useful taxonomy of deep learning approaches for imaging inverse problems, organised along two axes: knowledge of the forward model and availability of training data. Purely data-driven methods (end-to-end CNNs) can achieve competitive reconstruction quality when large, well-matched training sets are available, but they can be unstable to distribution shifts and lack interpretability. Deep unfolding, by contrast, preserves the physics of the forward model within the network architecture, requires fewer training samples, and tends to generalise better to unseen conditions \citep{monga2021}. For quantum imaging, where experimental training data is scarce and the forward measurement model is well characterised, the model-based unfolding approach is particularly attractive.

\subsection{Deep Unfolding for Ghost Imaging}

The application of deep unfolding to ghost imaging introduces a specific technical challenge: the measurement matrices in computational ghost imaging are non-negative (composed of illumination pattern intensities), unlike the random Gaussian matrices assumed by standard CS theory. \citet{cheng2022} addressed this mismatch by applying singular value decomposition (SVD) preprocessing to the ghost imaging measurement matrix to obtain a semi-orthogonal measurement matrix, and then feeding the transformed measurements into an ISTA-Net+ architecture. This combination improved both anti-noise performance and reconstruction fidelity at low sampling rates compared to direct application of standard deep unfolding.

\citet{zou2024} proposed MPDU-Net, a deep unfolding network designed specifically for single-pixel imaging systems. MPDU-Net integrates multiple prior information, including spatial, spectral, and structural priors, into each unfolding stage through dedicated learned prior modules. The multi-prior approach improved reconstruction quality at very low sampling ratios compared to single-prior unfolding methods.

These works focus on computational ghost imaging with classical correlations; extending deep unfolding architectures to exploit genuine quantum correlations in the measurement model, for example by incorporating the photon-pair statistics of SPDC sources into the forward operator, is an open problem.

\subsection{Entanglement-Assisted Measurement Optimisation}

The end-to-end optimisation approach of \citet{wang2019}, which jointly learned illumination patterns and the reconstruction network for computational ghost imaging, provides a blueprint for measurement design in quantum systems. Extending this framework to quantum imaging would involve treating the SPDC source parameters (pump wavelength, crystal orientation, phase-matching conditions) and detection basis choices as differentiable variables within the optimisation. While technically challenging, such an approach could yield further measurement reductions by tailoring the quantum measurement process to the reconstruction algorithm.

This connects to the broader field of quantum state tomography, where compressed sensing has been applied to reconstruct quantum states from incomplete measurement sets with provable recovery guarantees. Neural networks have recently been used to improve tomographic reconstruction from informationally incomplete data, suggesting that similar gains may be achievable in quantum imaging when the measurement strategy and reconstruction algorithm are co-designed.
